Factors affecting health sector expenditure in OECD countries

### 2025-05-03 code/analysis-code/statistical-analysis.qmd
removing underscore

```{r}
# Save the table as a HTML file
html_file <- here("products", "supplementary-files", "regression_results.html")
save_kable(table_html, file = html_file)

@@

modelsummary(
  model,
  output = here("results", "tables", "primary_regression_results.png"),
  title = "This table represents the primary regresssion model",
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  notes = list(
    "Standard errors are shown in parentheses.",
    "Significance levels: * p < 0.1, ** p < 0.05, *** p < 0.01."
  )
)

>>>>

```{r}
# Save the table as a HTML file
html_file <- here("results", "supplementary-tables", "regression_results.html")
save_kable(table_html, file = html_file)

@@

# Define a named vector for pretty variable names
pretty_names <- c(
  "(Intercept)" = "Intercept",
  "GDP_growth_annual_" = "GDP Growth (annual %)",
  "Income_share_held_by_lowest_20" = "Income Share (Lowest 20%)",
  "Control_of_Corruption_Estimate" = "Control of Corruption",
  "Life_expectancy_at_birth_total_years" = "Life Expectancy (years)",
  "Unemployment_youth_total__of_total_labor_force_ages_1524_modeled_ILO_estimate" = "Youth Unemployment (% of labor force, ages 15-24)",
  "Trade__of_GDP" = "Trade (% of GDP)",
  "Foreign_direct_investment_net_inflows_BoP_current_US" = "FDI Net Inflows (current US$)",
  "Access_to_electricity_rural__of_rural_population" = "Rural Electricity Access (% of rural population)",
  "Age_dependency_ratio__of_workingage_population" = "Age Dependency Ratio"
)

# Generate the table with formatted names
modelsummary(
  model,
  output = here("results", "tables", "primary_regression_results.png"),
  title = "",
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_rename = pretty_names,
  notes = list(
    "Standard errors are shown in parentheses.",
    "Significance levels: * p < 0.1, ** p < 0.05, *** p < 0.01."
  )
)

### 2025-05-03 code/eda-code/eda.qmd
removing underscore

# Function to create a scatter plot with correlation
create_corr_plot <- function(x_var, df, point_color) {
  cor_value <- round(cor(df[[x_var]], df$Current_health_expenditure_per_capita_current_US, use = "complete.obs"), 2)

  ggplot(df, aes_string(x = x_var, y = "Current_health_expenditure_per_capita_current_US")) +
    geom_point(color = point_color, alpha = 0.6) +  # Set color based on input
    geom_smooth(method = "lm", color = "red", se = FALSE) +
    labs(title = paste("Correlation:", cor_value), x = x_var, y = "Health Expenditure per Capita") +
    theme_minimal()
}

>>>>

# Function to create a scatter plot with correlation and formatted x-axis labels
create_corr_plot <- function(x_var, df, point_color) {
  # Create a named vector for neat variable names
  pretty_names <- c(
    "GDP_growth_annual_" = "GDP Growth (annual %)",
    "Income_share_held_by_lowest_20" = "Income Share held by lowest 20%",
    "Control_of_Corruption_Estimate" = "Control of Corruption Estimate",
    "Life_expectancy_at_birth_total_years" = "Life expectancy at birth (years)",
    "Literacy_rate_adult_total__of_people_ages_15_and_above" = "Adult literacy rate (% ages 15+)",
    "Trade__of_GDP" = "Trade (% of GDP)",
    "Foreign_direct_investment_net_inflows_BoP_current_US" = "FDI Net inflows (current US$)",
    "Age_dependency_ratio__of_workingage_population" = "Age Dependency Ratio (% of working-age population)"
  )

  cor_value <- round(cor(df[[x_var]], df$Current_health_expenditure_per_capita_current_US, use = "complete.obs"), 2)

  ggplot(df, aes_string(x = x_var, y = "Current_health_expenditure_per_capita_current_US")) +
    geom_point(color = point_color, alpha = 0.6) +
    geom_smooth(method = "lm", color = "red", se = FALSE) +
    labs(
      title = paste("Correlation:", cor_value), 
      x = pretty_names[x_var], 
      y = "Health Expenditure per Capita (current US$)"
    ) +
    theme_minimal()
}

### 2025-05-03 products/manuscript/Manuscript.qmd
removing underscore

```{r}
#| label: tbl-primary-regression-results
#| tbl-cap: "Primary Regression Results"
#| echo: FALSE
#| out.width: "70%"
knitr::include_graphics(here("results", "tables", "primary_regression_results.png"))
```

@@

```{r}
#| label: tbl-DW-test-results
#| tbl-cap: "Durbin Watson Test Results"
#| echo: FALSE
#| out.width: "30%"
knitr::include_graphics(here("results", "figures", "durbin_watson_test_results.png"))
```

>>>>

```{r}
#| label: tbl-primary-regression-results
#| tbl-cap: "Primary Regression Results"
#| echo: FALSE
#| out.width: "55%"
knitr::include_graphics(here("results", "tables", "primary_regression_results.png"))
```

@@

```{r}
#| label: tbl-DW-test-results
#| tbl-cap: "Durbin Watson Test Results"
#| echo: FALSE
#| out.width: "27%"
knitr::include_graphics(here("results", "figures", "durbin_watson_test_results.png"))
```
